The Astropy Project

### 2017-10-28 main.tex
comment out section that's realistically not going to get written
coordination stuff

\begin{abstract}
% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
% free to modify!
The \astropy project supports and fosters the development of open-source and open-development
\python packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the \astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the \astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate and support
development for a broader ecosystem of inter-operable packages.
We conclude with a future outlook of planned new features and directions for the
broader \astropy project.
\end{abstract}

@@

\subsection{Coordination of Astropy}
\inlinecomment{EJT}

@@

\subsubsection{Accuracy and comparison of coordinate system definitions}
% Erik?

>>>>

\begin{abstract}
% I (Adrian) took a first stab at the abstract, but it needs some work. Feel
% free to modify!
The \astropy project supports and fosters the development of open-source and openly-developed
\python packages that provide commonly-needed functionality to the astronomical
community.
A key element of the project is the \astropy core package, which serves as the
foundation for more specialized projects and packages.
In this article, we provide an overview of the organization of the \astropy
project and summarize key features in the core package as of the recent major
release, version 2.0.
We then describe the project infrastructure designed to facilitate and support
development for a broader ecosystem of inter-operable packages.
We conclude with a future outlook of planned new features and directions for the
broader \astropy project.
\end{abstract}

@@

\subsection{Coordination of Astropy}
From its inception, \astropy has required coordination to ensure the project as a whole and its coding efforts are consistent and reasonably efficient.
While many Python projects adopt a ``Benevolent Dictator For Life'' (BDFL) model, Astropy has instead opted for a coordination \emph{committee}.
This is in part due to the nature of the project as a large-scale collaboration between many contributors with many interests, and in part due to simply the amount of work that needs to get done.
In part for the latter reason, the project has expanded the committee from three to four members from 2016 on.

In the code itself, the coordination committee primarily acts to work toward consensus, or when consensus is difficult to achieve, generally acts as ``tie-breaker.''
The committee also oversees affiliated package applications to ensure they are in keeping with \astropy's vision and philosophy, as well as the associated processes procedures.
Additionally, the committee oversees the assignment of roles (primarily driven by already-existing contributions), and increasingly has acted as the ``face'' of the Project, providing contact with organizations like NumFOCUS (The body that holds any potential funding in trust for \astropy) or the AAS.

@@

%\subsubsection{Accuracy and comparison of coordinate system definitions}
% Erik?
